Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-29 Papers/ms.tex
comment on mass posterior
Include the substructure figure

In Figure~\ref{fig:simdata_masses}, we plot the joint posterior distribution
for the SIE mass within its critical ellipse and the total substructure mass
over the entire domain.

@@

>>>>

In Figure~\ref{fig:simdata_masses}, we plot the joint posterior distribution
for the SIE mass within its critical ellipse and the total substructure mass
over the entire domain. As one would expect, there is a strong dependence
between these two quantities in the posterior distribution, as mass in the
SIE can be traded off with mass in substructures to some extent, while
the model remains (loosely speaking) ``consistent with the data''.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures.pdf}
\caption{The simulated data, with substructure positions overlaid (a
Monte Carlo approximation to the posterior expectation of the empirical
measure).
\label{fig:substructures}}
\end{center}
\end{figure}
